---
title: "Boston Housing Data"
author: "Kyle Rozic"
date: "4/21/2021"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
```

## Packages required

```{r, message = F, warning = F}
library(plotly)
```

## Boston Housing Data

Data from [Kaggle](https://www.kaggle.com/vikrishnan/boston-house-prices)

- CRIM - per capita crime rate by town
- ZN - proportion of residential land zoned for lots over 25,000 sq.ft.
- INDUS - proportion of non-retail business acres per town.
- CHAS - Charles River dummy variable (1 if tract bounds river; 0 otherwise)
- NOX - nitric oxides concentration (parts per 10 million)
- RM - average number of rooms per dwelling
- AGE - proportion of owner-occupied units built prior to 1940
- DIS - weighted distances to five Boston employment centres
- RAD - index of accessibility to radial highways
- TAX - full-value property-tax rate per $10,000
- PTRATIO - pupil-teacher ratio by town
- B - 1000(Bk - 0.63)^2 where Bk is the proportion of black/African American individuals by town
- LSTAT - % lower status of the population
- MEDV - Median value of owner-occupied homes in $1000's

## Load Data

```{r}
bostonhousing <- read.csv('./data/housing.csv', header = F, sep = '')
colnames(bostonhousing) <- c('CRIM', 'ZN', 'INDUS', 'CHAS', 'NOX', 'RM', 'AGE', 'DIS', 'RAD', 'TAX', 'PTRATIO', 'B', 'LSTAT', 'MEDV')
head(bostonhousing)
```

## Correlate Housing Data to House Price

```{r}
plot_ly(bostonhousing, 
        x = bostonhousing$CRIM, 
        y = bostonhousing$MEDV, 
        z = bostonhousing$RM, 
        type = 'scatter3d', 
        mode = 'markers', 
        alpha = 0.5, 
        color = bostonhousing$RAD, 
        size = bostonhousing$TAX)
```

## Conclusion

This was mainly an experiment to visualize many variables in 1 plot. It starts to get pretty confusing when this many variables are in the plot but it may be useful depending on the data. With this data I can see that a high accessibility to radial highways (RAD, `yellow`) correlates well with per capita crime rate (CRIM, `x`).

**Have A Great Day Stranger!** 